State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-06 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to the parameter convergence plot
changes to the field estimation plot
editing the results and frequency analysis

The sensors were spaced in a regular square \dean{M $\times$ N} grid, the sensor width $\sigma^2_m$ was \dean{1.44} which equals \dean{$2$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \dean{$2.22$}~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field. 

@@

\subfigure[]{\includegraphics[scale=0.55]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.55]{./Graph/theta2Convergence.pdf}}

@@

Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \dean{??} ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \dean{??}. This confirms our separation of \dean{??} was enough to prevent problems associated with aliasing.

The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c). The peak power of the spatial frequency of the observations was approximately \dean{$??$}~dB. The cut-off frequency (-3~dB point) was taken to correspond to  approximately \dean{$??$}~dB. This provided a conservative estimate of the spatial bandwidth. The oversampling parameter $\rho_b$ was set to \dean{??} giving a minimum distance between basis functions of \dean{??} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field. Equation~\ref{eq:WidthCutOffRelationship} (where $sigma_{\phi}^2 = $ \dean{??}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.

\begin{figure*}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.} 
\end{figure*}
Following this, the distance between basis function, $\Delta_{phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. \mike{Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.}

@@

  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros. Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the non-reduced model the was used to generate data. \textbf{b.} The reconstructed estimated field of the reduced model. \textbf{c.} The absolute error between the true and reconstructed fields.}
\label{fig:FieldEstimate}
\end{figure*}

>>>>

The sensors were spaced in a regular square \parham{14 $\times$ 14} grid, the sensor width $\sigma^2_m$ was \parham{0.81} which equals \parham{$1.5$}~mm full width at half maximum, with spacing $\Delta_y$ equal to \parham{$1.5$}~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design that is sufficient to guarantee an accurate representation of the field can be achieved using the frequency analysis from Section~\ref{SpectralAnalysisSection} given access to the true field. 

@@

\subfigure[]{\includegraphics[scale=1]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[scale=1]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/theta2Convergence.pdf}}

@@

Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency of the field was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FieldFFT}(a) shows the spatial frequency of the field. The cut-off frequency, $\nu_c$, was taken to be \parham{0.24} ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of \parham{2.05}mm. This confirms our separation of \parham{1.5}mm was enough to prevent problems associated with aliasing.

The spatial frequency of the observations is shown in Figure~\ref{fig:FreqAnalysis}(c). The peak power of the spatial frequency of the observations was approximately \parham{$30.62$}~dB. The cut-off frequency (-3~dB point) was taken to correspond to  approximately \parham{$26.47$}~dB. This provided a conservative estimate of the spatial bandwidth equals to \parham{0.19} Hz. The oversampling parameter $\rho_b$ was set to \parham{1} giving a minimum distance between basis functions of \parham{2.63} to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The width of the basis functions was chosen such that the basis functions had sufficient overlap to represent the dynamic field. Equation~\ref{eq:WidthCutOffRelationship} (where $\sigma_{\phi}^2 = $ \parham{2.5}) was used to confirm the width of the basis functions was sufficiently small to capture the characteristics of the field.

\begin{figure*}
	\label{fig:FreqAnalysis} 
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{Frequency analysis of the. \textbf{a.} The spatial frequency response of a 1-dimensional neural field basis functions project. The symmetry of the field basis functions, connectivity kernel basis functions and sensors allow for the 1-dimensional representation of the spectral characteristics. The dashed line shows the cut-off frequency (-3 dB point). \textbf{b} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} Two 2-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field.} 
\end{figure*}
Following this, the distance between basis function, $\Delta_{\phi}$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 2.5, 2.63 mm full width at half maximum. \mike{Analysis said 0.44 from Parham's derivation, but 2.5 still overlaps and allows more high frequency details to be represented.}

@@

  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros. Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[scale=0.9]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.9]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the non-reduced model the was used to generate data. \textbf{b.} The reconstructed estimated field of the reduced model. \textbf{c.} The absolute error between the true and reconstructed fields.}
\label{fig:FieldEstimate}
\end{figure*}
